### 2024-07-31 conteudo/background/codeduplication.tex
space on T

\begin{itemize}
	\begin{item}
		\textbf{Type-1(T1):} The differences between F and G are in the context of revision of comments, variable names,
		white spaces, and any other kinds of irrelevant elements. Figure
		\ref{fig:type1} shows a typical example of Type-1 clone duplication 
		\citep{litreview}. 
	\end{item}
	\begin{item}
		\textbf{Type-2(T2):} The differences between F and G are the same as type-1, with the addition of 
		considering the addition and deletion of redundant codes. Figure
		\ref{fig:type2} shows a typical example of Type-2 code clone duplication  \citep{litreview}. 
	\end{item}
	\begin{item}
		\textbf{Type-3(T3):} The difference between F and G is the same as type-2, with the addition of considering 
		the reorder of code blocks, as well as statements within code blocks. Figure
		\ref{fig:type3} shows a typical example of 
		Type-3 code clone duplication \citep{litreview}. 
	\end{item}
	\begin{item}
		\textbf{Type-4(T4):} The difference between F and G is the same as type-3, with the addition of considering 
		changes in data structures, the order of operands/operators in expressions, or replacing part of codes 
		with equivalent composition. Figure
		\ref{fig:type4} shows a typical example of Type-4 code clone duplication \citep{litreview}. 
	\end{item}

>>>>

\begin{itemize}
	\begin{item}
		\textbf{Type-1 (T1):} The differences between F and G are in the context of revision of comments, variable names,
		white spaces, and any other kinds of irrelevant elements. Figure
		\ref{fig:type1} shows a typical example of Type-1 clone duplication 
		\citep{litreview}. 
	\end{item}
	\begin{item}
		\textbf{Type-2 (T2):} The differences between F and G are the same as type-1, with the addition of 
		considering the addition and deletion of redundant codes. Figure
		\ref{fig:type2} shows a typical example of Type-2 code clone duplication  \citep{litreview}. 
	\end{item}
	\begin{item}
		\textbf{Type-3 (T3):} The difference between F and G is the same as type-2, with the addition of considering 
		the reorder of code blocks, as well as statements within code blocks. Figure
		\ref{fig:type3} shows a typical example of 
		Type-3 code clone duplication \citep{litreview}. 
	\end{item}
	\begin{item}
		\textbf{Type-4 (T4):} The difference between F and G is the same as type-3, with the addition of considering 
		changes in data structures, the order of operands/operators in expressions, or replacing part of codes 
		with equivalent composition. Figure
		\ref{fig:type4} shows a typical example of Type-4 code clone duplication \citep{litreview}. 
	\end{item}
